Writing a reproducible paper with RStudio and Quarto

### 2023-03-23 paper.qmd
remove all references to stargazer.

-   ...also install the packages below using the code below [@knitr1; @knitr2; @knitr3; @kableextra; @hlavac2013stargazer; @modelsummary; @gt].

``` {{r}}
install.packages(c("knitr", "kableExtra",
                   "stargazer", "modelsummary", "gt", "gtsummary"))
```

```{r eval=F}
install.packages(c("knitr", "kableExtra",
                   "stargazer", "modelsummary", "knitr", "gt", "gtsummary"))
```

@@

<!-- the stargazer section is only shown when the output format is PDF and not HTML -->

>>>>

-   ...also install the packages below using the code below [@knitr1; @knitr2; @knitr3; @kableextra; @modelsummary; @gt].

``` {{r}}
install.packages(c("knitr", "kableExtra", "modelsummary", "gt", "gtsummary"))
```

```{r eval=F}
install.packages(c("knitr", "kableExtra",
                   "modelsummary", "knitr", "gt", "gtsummary"))
```

@@
